State of the Practice for Lattice Boltzmann Method Software

### 2022-03-25 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Update abstract in SOP for LBM to address Jacques's feedback (#135).

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of a set of 20 questions). From the measurement results, we ranked the
    software using the Analytic Hierarchy Process (AHP). Our ranking was roughly
    consistent with ranking the repositories by the number of GitHub stars,
    although the number one project by star count (Sailfish) is ranked 9th by
    our methodology. Our finding is that the state of the practice is healthy
    with 67\% of the measured packages ranking in the top five for at least one
    quality, the majority of LBM generated artifacts corresponding to general
    recommendations from research software developers, common utilization of
    version control (67\% of packages) and adoption of a quasi-agile development
    process.  Areas of best practice to potentially improve include adoption of
    continuous integration, API documentation and enforcement of programming
    style guides.  We interviewed four developers to gain insight into their
    current pain points. Identified challenges include lack of development time,
    lack of funding, and difficulty with ensuring correctness.  Developers are
    addressing these pain points by designing for change, circumventing the
    oracle problem and prioritizing documentation and usability.  For future
    best practices, we suggest the community consider the following: employing
    linters, conducting rigorous peer reviews, writing and submitting more
    papers on software, growing the number of contributors and augmenting the
    theory manuals to include more requirements relevant information.

>>>>

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of a set of 20 questions). From the measurement results, we ranked the
    software using the Analytic Hierarchy Process (AHP). Our ranking was roughly
    consistent with ranking by GitHub stars, suggesting at least a partial
    correlation between the use of best practices and popularity. We find the
    state of the practice to be healthy, with 67\% of the measured packages
    ranking in the top five for at least one quality, the majority of LBM
    generated artifacts corresponding to general recommendations from research
    software developers, common utilization of version control (67\% of
    packages) and adoption of a quasi-agile development process.  Areas of best
    practice to potentially improve include adoption of continuous integration,
    API documentation and enforcement of programming style guides.  We
    interviewed four developers to gain insight into their current pain points.
    Identified challenges include lack of development time, lack of funding, and
    difficulty with ensuring correctness.  Developers are addressing these pain
    points by designing for change, circumventing the oracle problem and
    prioritizing documentation and usability. For future improvements we suggest
    the following: employing linters, conducting rigorous peer reviews, writing
    and submitting more papers on software, growing the number of contributors
    by following current recommendations for open source projects, and
    augmenting the theory manuals to include more requirements relevant
    information.
